Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

    The synthetic stream's photometry is also simulated using a 12~Gyr, [Fe/H] =
    -1.35~dex NMIST isochrone \TODO{[cite brutus]}. The isochrone is truncated just
    short of the giant branch, and is sampled from uniformly along the isochrone
    (i.e., the initial mass function, $P(\gamma)$, is uniform) as well as with
    an intrinsic uniform 0.2~dex scatter orthogonal to the isochrone track. The
    isochrone is shifted by the stream's parallax modulus, which is derived from
    the astrometric distance track.  The background photometric coordinates are
    generated as a 2-dimensional Gaussian with non-zero covariance.  Thus, the
    synthetic data scenario described here generates a mock stream in
    astrometric coordinates and photometric coordinates, with density
    variations, a distance gradient which is consistent in parallax and distance
    modulus (i.e., magnitudes), all superimposed over a noisy field of
    background points in each astrometric and photometric dimension.

>>>>

    The synthetic stream's photometry is also simulated using a \variable{output/mock/isochrone_age_variable.txt},
    [Fe/H] = \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone \TODO{[cite brutus]}. The isochrone is truncated just
    short of the giant branch, and is sampled from uniformly along the isochrone
    (i.e., the initial mass function, $P(\gamma)$, is uniform) as well as with
    an intrinsic uniform 0.2~dex scatter orthogonal to the isochrone track. The
    isochrone is shifted by the stream's parallax modulus, which is derived from
    the astrometric distance track.  The background photometric coordinates are
    generated as a 2-dimensional Gaussian with non-zero covariance.  Thus, the
    synthetic data scenario described here generates a mock stream in
    astrometric coordinates and photometric coordinates, with density
    variations, a distance gradient which is consistent in parallax and distance
    modulus (i.e., magnitudes), all superimposed over a noisy field of
    background points in each astrometric and photometric dimension.
